PAO

### 2021-05-24 doc/sand/pao.tex

\section{Simple Examples}
\label{\detokenize{examples:simple-examples}}\label{\detokenize{examples::doc}}
We illustrate the PAO algebraic and compact representations with a series
of simple examples.  Consider the following bilevel problem introduced
by Bard \sphinxcite{bard98} (example 5.1.1):
 \begin{equation*}
 \begin{array}{lll}
 \min_{x \geq 0} & x - 4 y & \\
 \textrm{s.t.} & \min_{y \geq 0} & y\\
 & \textrm{s.t.} & -x -y \leq -3\\
 & & -2 x + y \leq 0\\
 & & 2 x + y \leq 12\\
 & & 3 x - 2 y \leq 4
 \end{array}
 \end{equation*}
This problem has has linear upper\sphinxhyphen{} and lower\sphinxhyphen{}level problems with different
objectives in each level.  Thus, this problem can be represented in
PAO using a Pyomo model representation or the \sphinxcode{\sphinxupquote{LinearMultilevelProblem}}
representation.

@@

\subsection{Bilevel Examples}
\label{\detokenize{representations/pyomo:bilevel-examples}}
Consider the following bilevel problem:
\label{equation:sand:eq-pao1} \begin{equation*}
 \textbf{Model PAO1}
 \begin{array}{ll}
 \min_{x\in[2,6],y} & x + 3 z \\
 \textrm{s.t.} & x + y = 10\\
 & \begin{array}{lll}
   \max_{z \geq 0} & z &\\
   \textrm{s.t.} & x+z &\leq 8\\
   & x + 4 z &\geq 8\\
   & x + 2 z &\leq 13
   \end{array}
 \end{array}
 \end{equation*}
This problem has has linear upper\sphinxhyphen{} and lower\sphinxhyphen{}level problems with different
objectives in each level.

@@

\subsection{Linear Bilevel Examples}
\label{\detokenize{representations/mpr:linear-bilevel-examples}}
We consider again the bilevel problem PAO1 \eqref{equation:sand:eq-pao1}.  This problem
has has linear upper\sphinxhyphen{} and lower\sphinxhyphen{}level problems with different objectives
in each level.

>>>>

\section{Simple Examples}
\label{\detokenize{examples:simple-examples}}\label{\detokenize{examples::doc}}
We illustrate the PAO algebraic and compact representations with a series
of simple examples.  Consider the following bilevel problem introduced
by Bard \sphinxcite{bard98} (example 5.1.1):
 \begin{equation*}
 \begin{array}{lll}
 \min_{x \geq 0} & x - 4 y & \\
 \textrm{s.t.} & \min_{y \geq 0} & y\\
 & \textrm{s.t.} & -x -y \leq -3\\
 & & -2 x + y \leq 0\\
 & & 2 x + y \leq 12\\
 & & 3 x - 2 y \leq 4
 \end{array}
 \end{equation*}
This problem has linear upper\sphinxhyphen{} and lower\sphinxhyphen{}level problems with different
objectives in each level.  Thus, this problem can be represented in
PAO using a Pyomo model representation or the \sphinxcode{\sphinxupquote{LinearMultilevelProblem}}
representation.

@@

\subsection{Bilevel Examples}
\label{\detokenize{representations/pyomo:bilevel-examples}}
Consider the following bilevel problem:
\label{equation:sand:eq-pao1} \begin{equation*}
 \textbf{Model PAO1}
 \begin{array}{ll}
 \min_{x\in[2,6],y} & x + 3 z \\
 \textrm{s.t.} & x + y = 10\\
 & \begin{array}{lll}
   \max_{z \geq 0} & z &\\
   \textrm{s.t.} & x+z &\leq 8\\
   & x + 4 z &\geq 8\\
   & x + 2 z &\leq 13
   \end{array}
 \end{array}
 \end{equation*}
This problem has linear upper\sphinxhyphen{} and lower\sphinxhyphen{}level problems with different
objectives in each level.

@@

\subsection{Linear Bilevel Examples}
\label{\detokenize{representations/mpr:linear-bilevel-examples}}
We consider again the bilevel problem PAO1 \eqref{equation:sand:eq-pao1}.  This problem
has linear upper\sphinxhyphen{} and lower\sphinxhyphen{}level problems with different objectives
in each level.
